Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-07-09 paper/figures.Rnw
Figure must be standalone for TIF conversion

<<map, results='hide'>>=
    library(mapproj)
    tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    US.counties = readOGR(dsn="../data/maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
    US.counties = US.counties[US.counties$STATEFP == "09",]
    county.data = US.counties@data %>%
        mutate(id=rownames(.)) %>%
        data.table() %>%
        mutate(highRSV=ifelse(NAME %in% lowIncidenceCounties, FALSE, TRUE))

@@

<<seasonByRegion, results='hide'>>=
    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)

@@

<<coverageByRegionAAP, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)

@@

<<coverageByRegionAAPInsight, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10)

@@

    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE) %>%
        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))

@@

<<coverageByRounding, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)

@@

<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat)) %>%
        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:4], levels(strat)[8:10])))

@@

<<onsetOffsetByYear, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    data = stateThresholdsByWindow %>% 
        melt(id=c("epiyear")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        cast(epiyear + variable ~ pctile) %>%
        mutate(variable=factor(variable, levels=onOffLevels))

>>>>

<<map, results='hide'>>=
    library(mapproj)
    tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)
    US.counties = readOGR(dsn="../data/maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
    US.counties = US.counties[US.counties$STATEFP == "09",]
    county.data = US.counties@data %>%
        mutate(id=rownames(.)) %>%
        data.table() %>%
        mutate(highRSV=ifelse(NAME %in% lowIncidenceCounties, FALSE, TRUE))

@@

<<seasonByRegion, results='hide'>>=
    tikz(sprintf("%s/seasonByRegion.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)

@@

<<coverageByRegionAAP, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAP.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)

@@

<<coverageByRegionAAPInsight, results='hide'>>=
    tikz(sprintf("%s/coverageByRegionAAPInsight.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight, pointsize=10, standAlone=TRUE)

@@

    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10, standAlone=TRUE)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE) %>%
        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))

@@

<<coverageByRounding, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRoundingRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10, standAlone=TRUE)

@@

<<coverageByRegionWithSliding, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRegionRegimenWithSliding.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10, standAlone=TRUE)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, !grepl("county", strat)) %>%
        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:4], levels(strat)[8:10])))

@@

<<onsetOffsetByYear, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/onsetOffsetByYear.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10, standAlone=TRUE)
    data = stateThresholdsByWindow %>% 
        melt(id=c("epiyear")) %>%
        cSplit(c("variable"), c(".")) %>%
        rename(variable=variable_1, pctile=variable_2) %>%
        cast(epiyear + variable ~ pctile) %>%
        mutate(variable=factor(variable, levels=onOffLevels))
